EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-14 draft.tex
More explanation of BBOB figure
@JJ please check it is super clear :angel

  \includegraphics[width=0.30\textwidth]{GAOnly_f005}&
  \includegraphics[width=0.30\textwidth]{PSOOnly_f005}&
  \includegraphics[width=0.30\textwidth]{GAPSO_f005}\\
  \end{tabular}
  \vspace{-3ex}
   \caption{
Scaling of running time with problem dimension to reach certain target values $\Delta f$. Lines:
average runtime (aRT); Cross ($+$): median runtime of successful runs to reach
the most difficult target that was reached at least once (but not always);
Cross (\textcolor{red}{$\times$}): maximum number of f-evaluations in any trial. Notched boxes:
interquartile range with median of simulated runs; all values are divided by
dimension and plotted as $log_{10}$ values versus dimension.
% More explanation for those not familiar with BBOB - JJ
}
\label{fig:bbob}
\end{figure*}

>>>>

  \includegraphics[width=0.30\textwidth]{GAOnly_f005}&
  \includegraphics[width=0.30\textwidth]{PSOOnly_f005}&
  \includegraphics[width=0.30\textwidth]{GAPSO_f005}\\
  \end{tabular}
  \vspace{-3ex}
   \caption{
Scaling of expected runtime (RT defined as the number of function
evaluations to reach a target function value for the first time) for  
each problem dimension. Target values $\Delta f$ = 10, 1, $10^{-1}$, $10^{-2}$,$10^{-3}$,$10^{-5}$,$10^{-8}$
(the exponent and line colors are given in the legend of $f_1$ in the top row). 
Lines are the average RT (aRT); Cross ($+$): median RT of successful runs to reach
the most difficult target that was reached at least once (but not always);
Cross (\textcolor{red}{$\times$}): maximum number of f-evaluations in any trial. 
All values are divided by dimension and plotted as $log_{10}$ values versus dimension.
% More explanation for those not familiar with BBOB - JJ
% I think is more clear? - M
}
\label{fig:bbob}
\end{figure*}
